---
title: "D3 Bar Graph"
author: "Nathan Frey"
date: "January 23, 2016"
output: html_document
---

This is my attempt to make a bar graph using R and D3. I'm putting my work on GitHub to keep it simple

```{r}
library(htmlwidgets)
library(roxygen2)
library(devtools)
library(jsonlite)
library(networkD3) #For examples and MisLinks and MisNodes data

```
A quick function to examine data:  
```{r}
lu<- function(x){length(unique(x))}

```
Get the data:
```{r}
set.seed(123)
numz<- round(runif(15, min=3, max=20),0)
numz
```

Now, we'll set up the file scaffolding. I need to find out if running these after I have done work on the widget JavaScript code and R code will wipe out my work. I'll just run this onceInstead, only run the devtools::install() to rebuild the widget and launch it.  
```{r}
create("d3BarGraph") #create the package skelton
htmlwidgets::scaffoldWidget("d3BarGraph") 
```

Now make the necessary edits to the .yaml file, pyramid.R file, and pyramid.js files.   

I edited the yaml file, added the D3 library as a dependecy, and then told it to use the style.css as the stylesheet. I am not sure if this is correct, but I am going to give it a try.

The next steps are to build the package, as per Hilary Parker's guide...  
```{r}
getwd()


#If needed for testing:
setwd("/Users/Nathan/Dropbox/R Projects Personal/d3BarGraph")

document() #create the man folder, automatically generate the pyramid.Rd file
```

Now to install and run the package! Hopefully it works (Fingers crossed)  

```{r}
getwd()
setwd("..")
getwd()
install("d3BarGraph")
```

Let's load the library and make a go at it!

```{r}
library(d3BarGraph)
d3BarGraph::d3BarGraph(numz, width = 300, height = 300) #somehow fails. How do I find out why/where?

```


For quickly rebuilding and attempting to launch:  
```{r}
setwd("/Users/Nathan/Dropbox/R Projects Personal/d3BarGraph")
document() #create the man folder, automatically generate the pyramid.Rd file
setwd("..")
install("d3BarGraph")
library(d3BarGraph)
d3BarGraph::d3BarGraph(numz, width = 300, height = 300) #somehow fails. not sure ATM...
```


































































































